---
title: "Diversify Into Alternatives"
author: "Yutao Jin"
date: "13 October 2020"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(ggthemes)
library(readxl)
library(ggrepel)
library(corrplot)
library(quadprog)
```


> When covid-19 outbreak, we have entered a new normal with low yield. Under the circumstances, many investors go into a dilemma. On one hand, to hunt for high-yield, investors should add risk to portfolio. On the other hand, with geopolitical risks, covid-19, and economic recession, there are so many uncertainties forward. To solve this dilemma, I think one important step is diversify into alternatives. In this blog, let's see how alternatives benefit our asset allocation.

# Data Initialization

My data comes from [J.P. Morgan Long-Term Capital Market Assumptions](https://am.jpmorgan.com/hk/en/asset-management/adv/insights/portfolio-insights/long-term-capital-market-assumptions/). In this session, I use three datasets. `assets` contains expected return and annual volatility information of different asset classes. `corr` and `covariance` store correlation and covariance data of these assets.

```{r load-assets-data}
# Load assets data
assets <- read_excel("C:/Data Analytics/my_website/content/projects/SAA/assets_risk_return.xlsx")
glimpse(assets)
```

```{r load-correlation-data}
# Load correlation data
corr <- read_excel("C:/Data Analytics/my_website/content/projects/alternatives/assets_correlation.xlsx")
glimpse(corr)
```

```{r}
# Load covariance data
covariance <- read_excel("C:/Data Analytics/my_website/content/projects/SAA/assets_covariance.xlsx")
glimpse(covariance)
```


# Correlation among alternatives and traditional assets




```{r,fig.width=10,fig.height=10}
# Convert dataframe into correlation matrix
corr_matrix=data.matrix(corr[1:17,2:18])
rownames(corr_matrix)<-colnames(corr_matrix)

# Visualize correlation

corrplot(corr_matrix,
         method="color",
         tl.cex=0.8,
         tl.col="black",
         addCoef.col="black")
```



# Adding alternatives to portfolio


```{r}
selected_assets<-assets %>%
  filter(Assets=="AC World Equity"|
           Assets=="World Government Bonds hedged"|
           Assets=="Macro Hedge Funds")
```


```{r}
# mean return of asset
r_equities=assets[assets$Assets=="AC World Equity","Expected_Return"]
r_bonds=assets[assets$Assets=="World Government Bonds hedged","Expected_Return"]
r_alternatives=assets[assets$Assets=="Macro Hedge Funds","Expected_Return"]

# standard deviation of portfolio
sigma_equities=assets[assets$Assets=="AC World Equity","Annual_Volatility"]
sigma_bonds=assets[assets$Assets=="World Government Bonds hedged","Annual_Volatility"]
sigma_alternatives=assets[assets$Assets=="Macro Hedge Funds","Annual_Volatility"]
cov_equities_bonds=covariance[covariance$Assets=="AC World Equity","World Government Bonds hedged"]
cov_equities_alternatives=39.69
cov_bonds_alternatives=3.72

# Construct equities-bonds portfolio 
i=0
while(i<=1){
  r=r_equities*i+r_bonds*(1-i)
  sigma=sqrt(i^2*sigma_equities^2+(1-i)^2*sigma_bonds^2+i*(1-i)*2*cov_equities_bonds)
  assets<-rbind(assets,data.frame(Assets=paste(round(i*100),"/",round(100-i*100)),Class="Portfolio",Expected_Return=r,Annual_Volatility=sigma))
  i=i+0.1
}

```

```{r}
# Filter necessary data
equities_bonds<-assets %>%
  filter(Class=="Portfolio"|
           Assets=="AC World Equity"|
           Assets=="World Government Bonds hedged")

# Create the plot
plot1<-ggplot(equities_bonds,aes(x=Annual_Volatility,y=Expected_Return))+
  
  # Line of efficient frontier
  geom_line()+
  
  # Point of 60/40 portfolio, equities, and bonds
  geom_point(data=equities_bonds[equities_bonds$Assets=="30 / 70",],size=3,colour="blue")+
  geom_point(data=equities_bonds[equities_bonds$Assets=="50 / 50",],size=3,colour="blue")+
  geom_point(data=equities_bonds[equities_bonds$Assets=="70 / 30",],size=3,colour="blue")+
  geom_point(data=equities_bonds[equities_bonds$Assets=="AC World Equity",],size=2)+
  geom_point(data=equities_bonds[equities_bonds$Assets=="World Government Bonds hedged",],size=2)+
  
  # Add label to points
  geom_text_repel(data=equities_bonds[equities_bonds$Assets=="30 / 70",],aes(x=Annual_Volatility,y=Expected_Return,label=Assets),colour="Black",vjust=-1)+
  geom_text_repel(data=equities_bonds[equities_bonds$Assets=="50 / 50",],aes(x=Annual_Volatility,y=Expected_Return,label=Assets),colour="Black",vjust=-1)+
  geom_text_repel(data=equities_bonds[equities_bonds$Assets=="70 / 30",],aes(x=Annual_Volatility,y=Expected_Return,label=Assets),colour="Black",vjust=-1)+
  geom_text_repel(data=equities_bonds[equities_bonds$Assets=="AC World Equity",],aes(x=Annual_Volatility,y=Expected_Return,label=Assets),colour="Black")+
  geom_text_repel(data=equities_bonds[equities_bonds$Assets=="World Government Bonds hedged",],aes(x=Annual_Volatility,y=Expected_Return,label=Assets),colour="Black",hjust=-0.05)+
  
  # Set title, and axis label
  labs(title="Equities-Bonds Portfolio",
       x="Volatility",
       y="Compounded return (%)")+
  theme_minimal(base_size=9)

plot1
```

```{r}
plot2<-plot1+
  geom_point(data=selected_assets[selected_assets$Class=="Alternatives",],aes(x=Annual_Volatility,y=Expected_Return),size=2)+
  geom_text_repel(data=selected_assets[selected_assets$Class=="Alternatives",],aes(x=Annual_Volatility,y=Expected_Return,label=Assets))

plot2

```


























# Reference






